Adopting agile in the large: motivations, success factors and challenges

### 2014-04-29 journal/article.tex
Lack of coaching/training

@@

@@

>>>>

% ADD THIS QUOTATION:
% [P21]
% The development projects require continues maintenance and support. In addition,
% the team was working on a new project with firm deadlines. The work environment
% was very demanding and team worked under pressure to produce products according
% to the planned schedule.
% Scrum adoption process started while every member of the team was engaged in
% his/her everyday tasks. With such work pressure the daily Scrum meetings added
% extra pressure to the employees. They used to meet weekly and later twice a
% month and then only when required and usually after working hours. As teams
% started to skip daily meetings it also affected the learning process of scrum
% between the team members. This eventually led to the failure of learn and
% implement concept of the agile method.

@@

% Lack of resources

@@

C: Lack of resoruces for training/coaching/piloting

* There was not enough coaches to spread the transformation
* New coaches from within the organization
[P1]
However the number of teams was large, and there were insufficient trained
coaches to go around, so new coaches were being trained from within the
organization, an important aspect of which was an ‘agile boot camp’.

* Not enough coaches --> Funding constraint
* ``the demand for training and coaching was simply outstripping supply''
* Teams go ahead by them selves, and fail
* The need for more coaches was proven by showing figures of increased productivity for coached teams
[P6]
We were spread so thin that we lost track of the team trainings in progress and
were unable to keep up with demand. The whole program was in danger of
imploding. We said “no” to teams who were requesting help thinking that might
stem the tide. Many of those teams went ahead We frequently ran into one reason
that many Scrum implementations fail;

Unfortunately, our funding and headcount just weren’t sufficient to support the
accelerating adoption.  We had funding from various parts of the organization,
including the internal professional development organization, but the demand for
training and coaching was simply outstripping supply. We needed to show that
well-coached Scrum teams were worth the cost of coaching. For that, we would
need metrics.

* Damage due to lack of coaching --> The legacy of old model does damage if the team is not coached for agile
* Lack of coaches impeded repetition of success
* Hard to find good coaches
[P9] <--> [P6]
Without proper coaching however, the success of these informal teams met with
mixed results over the longer term.  In retrospect, many of these teams did
damage to themselves by improperly applying Agile techniques, particularly when
command and control mechanisms were still in place.

* Coaches were not hired --> Financial constraint
* A proper piloting effort was not granted
* Lack of training demotivated
[P20]
Entity S management recognized the need to hire a contractor as an agile master.
However the position was not filled due to financial constraints.

”why investing too much and wasting time and resources for a pilot project if
the Scrum method promises success?”.
Later after few weeks of direct adoption of Scrum, the team started to face
tremendous difficulties and started gradually going back to their previous work
method to catch up with late deadlines.

The employees were unmotivated by lack of resources and lack of training.

* There was no coach --> Financial constraints
* Lack of training
[P21]
Missing Agile Master: Management recognized the need to have a coach. However
the position was not filled due to financial constraints and senior software
managers from within entity S took the role as the Scrum Master.

The employees were unmotivated by lack of resources and lack ofrecognition of
their efforts to improve the software development method.

* Not enough coaches
[P23]
The Cookbook had done an excellent job of establishing a baseline understanding
of Agile Delivery approaches but it had also stimulated a wave of demand from
project teams asking for more information and guidance. BT’s “jam” – a team of
just two coaches in Agile Delivery - was very thinly spread, especially given
the scale of BT Exact’s workforce. Ironically, the success of these initiatives
meant that BT again found itself with a shortage of “lumps” in its “jam”.

* ``not enough people with agile experience to lead by example and/or mentor the non-agile developers''
* Too few people with agile experience
[P37]
As I considered where to begin, I gained my first ally. Another coach was
floating from team to team trying to provide support for the transformation. The
two of us had many conversations about the problems the team was having and came
up with two leading problems to tackle. One: we just did not have enough people
with agile experience to lead by example and/or mentor the non-agile developers.

* Shortened training led to motivation issues
[P45]
Many teams who had participated in the shortened training struggled later with
communication and motivation issues. It turned out that in contrast to the pilot
phase too few Scrum mentors were available to deal with the numerous team
problems. To overcome these problems team training sessions were extended to one
day per team and the “lean mentor” role was created. Lean mentors underwent
in-depth training in Scrum, lean methodologies, and communication. Scrum master
and product ownertraining sessions were extended to two days each.

* Too few coaches
* Coaches with too little experience may do harm to the agile model --> Now enforcing standards and certification
[P47]
The number of Agile projects and apprentice coaches is out pacing the number of
mentor coaches. Many people being put in the apprentice coach position are more
accustomed to traditional project practices. These factors contribute to
apprentices potentially gaining the wrong type of experience to enable them to
be an effective coach.

* Too little coaches --> Coaches did not have time to follow up with the team
* Too little training --> There are no trainers available
[P49]
As mentioned, there was no meaningful training in XP except for those projects
that went to Offsites. Even though some fifty or more Offsites were held, this
represented perhaps 30\% or less of all project teams. In order to empower
employees, training is key; its lack prevented the majority of employees from
truly understanding XP, let alone using it effectively. Training certainly could
have been done “on-the-job” by experienced XP coaches, but there were virtually
none at Qwest available to work with project teams. Offsites became the only
form of such training and it was clearly inadequate to drive largescale change.

Implementing XP without coaching will not work unless the team environment is
already very favorable, such as having developers who have already used XP
effectively and others who really want to try it.
